clean environment space
```{r}
rm(list=ls())
gc(reset=TRUE)
```

intall and loading library
```{r}
if (!require(MASS)) install.packages("MASS")
if (!require(reshape2)) install.packages("reshape2")
if (!require(reshape)) install.packages("reshape")
if (!require(dplyr)) install.packages("dplyr")
library(MASS) 
library(reshape2) 
library(reshape) 
library(dplyr)
```

prepare calendar datafile
```{r}
calendar <- read.csv("../../Data/calendar.csv")
calendar <- calendar[1:1941,c(2,7:11)]
head(calendar)
dim(calendar)
```

find week_id, the week_id is coresponding with wm_yr_wk
```{r}
calendar$d_id <- as.numeric(regmatches(calendar$d,regexpr("[[:digit:]]+",calendar$d)))
calendar$week_id <- ceiling(calendar$d_id / 7) 
```

create dummy variables for events
```{r}
calendar$Sporting <- ifelse(calendar$event_type_1 == "Sporting" | calendar$event_type_2 == "Sporting", 1,0)
calendar$Cultural <- ifelse(calendar$event_type_1 == "Cultural" | calendar$event_type_2 == "Cultural", 1,0)
calendar$Religious <- ifelse(calendar$event_type_1 == "Religious" | calendar$event_type_2 == "Religious", 1,0)
calendar$National <- ifelse(calendar$event_type_1 == "National" | calendar$event_type_2 == "National", 1,0)
```

group the weekly data
```{r}
calendar.GB <- calendar %>% group_by(wm_yr_wk,week_id) %>% summarise(Cultural=max(Cultural),Sporting=max(Sporting),Religious=max(Religious),National=max(National))
head(calendar.GB)
dim(calendar.GB)
```

prepare the sales datafile
```{r}
sales <- read.csv("../../Data/sales_train_evaluation.csv")
sales <- sales[,c(2,5,7:1947)]
head(sales)
dim(sales)
```

melt to transpose day as rows instead of column
```{r}
sales.melt <- melt(sales,id=c("item_id","store_id"))
head(sales.melt)
dim(sales.melt)
```

find week_id, the week_id is coresponding with wm_yr_wk 
```{r}
sales.melt$d_id <- as.numeric(regmatches(sales.melt$variable,regexpr("[[:digit:]]+",sales.melt$variable)))
sales.melt$week_id <- ceiling(sales.melt$d_id / 7) 
```

leave only meaningful columns 
```{r}
sales.melt <- sales.melt[,c(1,2,4,6)]
```

group sales get weekly sale
```{r}
sales.GB <- sales.melt %>% group_by(item_id,store_id,week_id) %>% summarise(weekly_sale=sum(value))
head(sales.GB)
dim(sales.GB)
```

merge both sales and calender by week_id
```{r}
sales.combine <- merge(x = calendar.GB, y = sales.GB, all.y = TRUE)
sales.combine <- sales.combine[,c("wm_yr_wk","week_id","store_id","item_id","Cultural","Sporting","Religious","National","weekly_sale")]
head(sales.combine)
dim(sales.combine)
```
clean datasets to speed next task
```{r}
rm(list= setdiff(ls(),"sales.combine"))
gc(reset=TRUE)
```
output dataframe as task 1 and clean RAM
```{r}
write.csv(sales.combine,"../../Data/task_1.csv")
rm(list=ls())
gc(reset=TRUE)
```
