##summarizing sales for each store/item by week
```{r}
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(reshape2)))
suppressWarnings(suppressMessages(library(dplyr)))
```


using calendar to get week_id from wm_yr_wk
```{r}
calendar <- read.csv("../../Data/calendar.csv")
calendar <- calendar[1:1941,c(2,7)]
# find week_id, the week_id is corresponding with wm_yr_wk
calendar <- calendar %>%
  mutate(day = as.numeric(gsub('d_','',d))) %>%
  mutate(week_id = ceiling(day/7)) 

calendar <- calendar[,c(1,4)] %>%
  distinct()

#head(calendar,10)
```

merge week_id from calendar onto price
```{r}
price <- read.csv('../../Data/sell_prices.csv')
price_week <- merge(price,calendar, by.y = "wm_yr_wk")
price_week <- price_week[,c("wm_yr_wk","week_id","store_id","item_id","sell_price")] %>%
  arrange(week_id,store_id,item_id)

rm(calendar)
rm(price)
view(head(price_week,30))
```

write CSV for price by week as task 2
```{r}
write.csv(price_week,"../../Data/task_2.csv")
```

## you can stop here and have all the data required to be paired with data from task 1







## below I added weekly number of sales and revenue into the data
read sales data and remove junk
```{r}
sales <- read.csv('../../Data/sales_train_evaluation.csv')
sales<- sales[,-c(1,3:4,6)]
#head(sales,10)
```

melt, reformat day column, add week_id to sales_day data
```{r}
sales_day <- melt(sales) %>%
  rename(day = variable) %>%
  rename(sales = value) %>%
  mutate(day = as.numeric(gsub('d_','',day))) %>% #remove "d_" from day column and make format to number
  mutate(week_id = ceiling(day/7))  #creating the week number

rm(sales)
#head(sales_day,10)
```

create weekly sale amounts
```{r}
sales_week <- sales_day %>%
  group_by(item_id, store_id, week_id) %>%
  summarize(weekly_sale = sum(sales))

rm(sales_day)
view(head(sales_week,30))
```

combine price and sales, create revenue
```{r}
revenue_week <- merge(price_week,sales_week) %>%
  mutate(revenue = sell_price * weekly_sale) %>%
  arrange(store_id,item_id,week_id)
  
revenue_week <- revenue_week[,c("wm_yr_wk","week_id","store_id","item_id","sell_price","weekly_sale","revenue")]

view(head(revenue_week,30))
```

write a CSV of weekly revenue
```{r}
rm(price_week)
rm(sales_week)
write.csv(revenue_week,"../../Data/task_2_with_sales_and_revenue.csv")
```

