Pull in data from part 4_2
```{r}
rm(list=ls())
gc(reset=TRUE)

if (!require(tidyverse)) install.packages("tidyverse")
suppressMessages(suppressWarnings(library(tidyverse)))

task42 <- read.csv('../../Data/task_4_2.csv')
View(head(task42,30))
#glimpse(task42)
```


make models in below fashion:
model1: Y ~ X1+X2 + interaction term
model2: Y ~ logX1 + logX2 + interaction term
model3: Y ~ logX1 + X2 + interaction term 
model4: Y ~ X1 + logX2 + interaction term
where Y: weekly revenue  X1: Price Change  X2: Amazon Price


create interaction terms for each model and group x variable columns for each model
```{r}
task42 <- task42 %>%
  mutate(int1 = pct_change_price*amzn_price) %>%
  mutate(int2 = log_pct_change*log_amzn_price) %>%
  mutate(int3 = log_pct_change*amzn_price) %>%
  mutate(int4 = pct_change_price*log_amzn_price)


x_1 <- c("pct_change_price", "amzn_price", "int1")
x_2 <- c("log_pct_change", "log_amzn_price", "int2")
x_3 <- c("log_pct_change", "amzn_price", "int3")
x_4 <- c("pct_change_price", "log_amzn_price", "int4")
```


Split for training and validation
```{r}
set.seed(8675309)
smpl.size <- floor(0.7 * nrow(task42))
train_ind <- sort(sample(nrow(task42), size = smpl.size))
task42_sub <- task42[train_ind,]
valid_data <- task42[-train_ind,]
```






##model1
pct_change_price & amzn_price & int1
```{r}
model_1 <-task42_sub %>% select(wm_yr_wk,Cultural:weekly_revenue,store_id_CA_1:store_id_WI_2,item_on,one_of(x_1))
lm1 <- lm(weekly_revenue ~ .,data = model_1)
summary(lm1)
plot(lm1)
r2_1 <- summary(lm1)$adj.r.squared
```

predict and validate
```{r}
valid_data$pred1 <- predict(lm1, newdata = valid_data, type = 'response')

model_1_valid <- 100*mean((valid_data$pred1-valid_data$weekly_revenue)/valid_data$weekly_revenue)
model_1_valid
```

check cooks distance - no outliers
```{r}
cd <- cooks.distance(lm1)
which(cd>1) #no results, no outliers
```




##model2
log_pct_change & log_amzn_price & int2
```{r}
model_2 <-task42_sub %>% select(wm_yr_wk,Cultural:weekly_revenue,store_id_CA_1:store_id_WI_2,item_on,one_of(x_2))
lm2 <- lm(weekly_revenue ~ .,data = model_2)
summary(lm2)
plot(lm2)
r2_2 <- summary(lm2)$adj.r.squared
```

check cooks distance -no outliers
```{r}
cd <- cooks.distance(lm2)
which(cd>1) #no results, no outliers
```

predict and validate
```{r}
valid_data$pred2 <- predict(lm2, newdata = valid_data, type = 'response')
model_2_valid <- 100*mean((valid_data$pred2-valid_data$weekly_revenue)/valid_data$weekly_revenue)
model_2_valid
```





##model3
log_pct_change & amzn_price & int3
```{r}
model_3 <-task42_sub %>% select(wm_yr_wk,Cultural:weekly_revenue,store_id_CA_1:store_id_WI_2,item_on,one_of(x_3))
lm3 <- lm(weekly_revenue ~ .,data = model_3)
summary(lm3)
plot(lm3)
r2_3 <- summary(lm3)$adj.r.squared
```

check cooks distance -no outliers
```{r}
cd <- cooks.distance(lm3)
which(cd>1) #no results, no outliers
```

predict and validate
```{r}
valid_data$pred3 <- predict(lm3, newdata = valid_data, type = 'response')
model_3_valid <- 100*mean((valid_data$pred3-valid_data$weekly_revenue)/valid_data$weekly_revenue)
model_3_valid
```





##model4
pct_change_price & log_amzn_price & int4
```{r}
model_4 <-task42_sub %>% select(wm_yr_wk,Cultural:weekly_revenue,store_id_CA_1:store_id_WI_2,item_on,one_of(x_4))
lm4 <- lm(weekly_revenue ~ .,data = model_4)
summary(lm4)
plot(lm4)
r2_4 <- summary(lm4)$adj.r.squared
```

predict and validate
```{r}
valid_data$pred4 <- predict(lm4, newdata = valid_data, type = 'response')
model_4_valid <- 100*mean((valid_data$pred4-valid_data$weekly_revenue)/valid_data$weekly_revenue)
model_4_valid
```

check cooks distance -no outliers
```{r}
cd <- cooks.distance(lm4)
which(cd>1) #no results, no outliers
```




## Summary
create df to output summary of models      THE WINNER IS MODEL 1
```{r}
df_summary <- data.frame("Model" = c("1","2","3","4"),
                         "Type" = c("x1+x2","log(x1)+log(x2)","log(x1)+x2","x1+log(x2)"),
                         "ADJ_Rs" = c(r2_1,r2_2,r2_3,r2_4),
                         "Relative Error" = c(model_1_valid,model_2_valid,model_3_valid,model_4_valid))
df_summary
```
