
This is part2 to build and validate models. My task is to build and validate four models:
logY ~X1+X2 + interaction term
logY~logX1+X2 + interaction term 
logY~logX1+logX2 + interaction term
logY~X1+logX2 + interaction term
where Y: weekly revenue X1: Amazon Price/Gas  X2: + Price Change

clean RAM read dataset 
```{r}
rm(list=ls())
gc(reset=TRUE)

walmart.sale.total <- read.csv("..//..//Data//task_4_2.csv")

# set.seed(10086)
# samples <- sample(nrow(walmart.sale.total),size = floor(0.7 * nrow(walmart.sale.total)),replace=FALSE)
# length(samples)
# walmart.sale <- walmart.sale.total[samples,]
# walmart.test <- walmart.sale.total[-samples,]
# nrow(walmart.sale)
# nrow(walmart.test)

library(dplyr)
set.seed(10086)
smpl.size <- floor(0.7 * nrow(walmart.sale.total))
train_ind <- sample(nrow(walmart.sale.total), size = smpl.size)
walmart.sale <- walmart.sale.total[train_ind,]
walmart.test <- walmart.sale.total[-train_ind,]
```
model#5: logY ~X1+X2
```{r}

model.5 <- lm(log_weekly_revenue ~ wm_yr_wk+ store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+pct_change_price+amzn_price+item_on,data=walmart.sale)
summary(model.5)
plot(model.5)


model.5.1 <- lm(log_weekly_revenue ~  store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+pct_change_price+amzn_price+item_on,data=walmart.sale)
summary(model.5.1)
plot(model.5.1)
```

Model5: Cook's distance remove Outliers
```{r}
cook_distance <-cooks.distance(model.5)
which(cook_distance >1)
```

model5: validate model 5 with predict weekly revenue, formula: (weekly_revenue_pred - weekly_revenue)/weekly_revenue
```{r}
walmart.test <- walmart.test %>% 
                  mutate(weekly_revenue_pred.5=predict(model.5,newdata=.,type="response")) %>% 
                  mutate(weekly_revenue_pred.5.1=predict(model.5.1,newdata=.,type="response"))
model.5.val <- mean((exp(walmart.test$weekly_revenue_pred.5)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.5.val.1 <- mean((exp(walmart.test$weekly_revenue_pred.5.1)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.5.val
model.5.val.1

```

model 6: logY~logX1+X2 + interaction term

```{r}

model.6 <- lm(log_weekly_revenue ~ wm_yr_wk+ store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+log_pct_change+amzn_price+item_on,data=walmart.sale)
summary(model.6)
plot(model.6)


model.6.1 <- lm(log_weekly_revenue ~  store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+log_pct_change+amzn_price+item_on,data=walmart.sale)
summary(model.6.1)
plot(model.6.1)


```


Model6: Cook's distance remove Outliers
```{r}
cook_distance <-cooks.distance(model.6)
which(cook_distance >1)
```

model6: validate model 5 with predict weekly revenue, formula: (weekly_revenue_pred - weekly_revenue)/weekly_revenue
```{r}
walmart.test <- walmart.test %>% 
                  mutate(weekly_revenue_pred.6=predict(model.6,newdata=.,type="response")) %>% 
                  mutate(weekly_revenue_pred.6.1=predict(model.6.1,newdata=.,type="response"))
model.6.val <- mean((exp(walmart.test$weekly_revenue_pred.6)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.6.val.1 <- mean((exp(walmart.test$weekly_revenue_pred.6.1)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.6.val
model.6.val.1

```


model 8: logY~logX1+logX2 + interaction term

```{r}
walmart.sale.7 <-  transform(walmart.sale,interaction.term=log_pct_change*max(Cultural,Sporting,National,Religious))

model.7 <- lm(log_weekly_revenue ~ wm_yr_wk+ store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+log_pct_change+log_amzn_price+item_on,data=walmart.sale)
summary(model.7)
plot(model.7)

model.7.1 <- lm(log_weekly_revenue ~  store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+log_pct_change+log_amzn_price+item_on,data=walmart.sale)
summary(model.7.1)
plot(model.7.1)

```


Model7: Cook's distance remove Outliers
```{r}
cook_distance <-cooks.distance(model.7)
which(cook_distance >1)
```

model7: validate model with predict weekly revenue, formula: (weekly_revenue_pred - weekly_revenue)/weekly_revenue
```{r}
walmart.test <- walmart.test %>% 
                  mutate(weekly_revenue_pred.7=predict(model.7,newdata=.,type="response")) %>% 
                  mutate(weekly_revenue_pred.7.1=predict(model.7.1,newdata=.,type="response"))
model.7.val <- mean((exp(walmart.test$weekly_revenue_pred.7)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.7.val.1 <- mean((exp(walmart.test$weekly_revenue_pred.7.1)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.7.val
model.7.val.1

```





model 7: logY~X1+logX2 
```{r}


model.8 <- lm(log_weekly_revenue ~ wm_yr_wk+ store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+pct_change_price+log_amzn_price+item_on,data=walmart.sale)
summary(model.8)
plot(model.8)

model.8.1 <- lm(log_weekly_revenue ~  store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+pct_change_price+log_amzn_price+item_on,data=walmart.sale)
summary(model.8.1)
plot(model.8.1)

```


Model8: Cook's distance remove Outliers
```{r}
cook_distance <-cooks.distance(model.8)
which(cook_distance >1)
```

model8: validate model with predict weekly revenue, formula: (weekly_revenue_pred - weekly_revenue)/weekly_revenue
```{r}
walmart.test <- walmart.test %>% 
                  mutate(weekly_revenue_pred.8=predict(model.8,newdata=.,type="response")) %>% 
                  mutate(weekly_revenue_pred.8.1=predict(model.8.1,newdata=.,type="response"))
model.8.val <- mean((exp(walmart.test$weekly_revenue_pred.8)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.8.val.1 <- mean((exp(walmart.test$weekly_revenue_pred.8.1)-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)

model.8.val
model.8.val.1

```

```{r}
model=c("model.5","model.6","model.7","model.8")
value=c(model.5.val,model.6.val,model.8.val,model.7.val)
r.square <- c(summary(model.5)$r.squared,summary(model.6)$r.squared,summary(model.8)$r.squared,summary(model.7)$r.squared)
table=data.frame(Model=model,Value=value,R.square=r.square)
table
```

