```{r}

library(dplyr)
df <- read.csv('../../Data/task_4_2.csv')
head(df)
```





```{r}

```



Train test split plan a
```{r}
set.seed(6203)
smpl.size <- floor(0.7 * nrow(df))
train_ind <- sample(nrow(df), size = smpl.size)
length(train_ind)
nrow(df) - length(train_ind)
```

Train test split plan b. It uses stratified split to make sure each store receives the same portion of training and testing data.
```{r}
if (!require(caret)) install.packages("caret")
library(caret)
set.seed(6203)
train_ind <- createDataPartition(df$store_id, p = 0.7, list = FALSE)
length(train_ind)
nrow(df) - length(train_ind)
```


log-linear model where y = log_revenue, x1 = amazon stock price. x2 = price change.

```{r}
df_model5 <- subset(df, select = -c(week_id, store_id, log_pct_change,store_id_WI_3, price_CA, price_WI, price_TX, gas_price, log_amzn_price))
# df_model5 <- transform(df_model5,inter=pct_change_price*(max(Cultural,Sporting,National,Religious)+1))
df_model5 <- df_model5[train_ind,]
df_test <- df_model5[-train_ind,]
model5 <- lm(log_weekly_revenue~. - weekly_revenue, data = df_model5)
summary(model5)
```

```{r}
df_test$pred <- predict(model5, newdata = df_test, type = 'response')
# mean((exp(df_test$pred)-exp(df_test$log_weekly_revenue))/exp(df_test$log_weekly_revenue))
mean((exp(df_test$pred) - df_test$weekly_revenue) / df_test$weekly_revenue)
```



log-log model where y = log_revenue, x1 = log_amazon stock price. x2 = price change.
```{r}
df_model6 <- subset(df, select = -c(week_id, store_id, log_pct_change, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, amzn_price))
# df_model6 <- transform(df_model6,inter=pct_change_price*max(Cultural,Sporting,National,Religious))
df_model6 <- df_model6[train_ind,]
df_test <- df_model6[-train_ind,]
model6 <- lm(log_weekly_revenue~.-weekly_revenue, data = df_model6)
summary(model6)
```


```{r}
df_test$pred <- predict(model6, newdata = df_test, type = 'response')

# mean((exp(df_test$pred)-exp(df_test$log_weekly_revenue))/exp(df_test$log_weekly_revenue))
mean((exp(df_test$pred) - df_test$weekly_revenue) / df_test$weekly_revenue)
```


log-log model where y = log_revenue, x1 = amazon stock price. x2 = log_price change.
```{r}
df_model8 <- subset(df, select = -c(week_id, store_id, pct_change_price, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, log_amzn_price))
# df_model8 <- transform(df_model8,inter=log_pct_change*max(Cultural,Sporting,National,Religious))
df_model8 <- df_model8[train_ind,]
df_test <- df_model8[-train_ind,]
model8 <- lm(log_weekly_revenue~.-weekly_revenue, data = df_model8)
summary(model8)
# plot(model8)
```


```{r}
df_test$pred <- predict(model8, newdata = df_test, type = 'response')
# df_model7$pred <- predict(model7, newdata = df_model7, type = 'response')
# mean((exp(df_test$pred)-exp(df_test$log_weekly_revenue))/exp(df_test$log_weekly_revenue))
mean((exp(df_test$pred) - df_test$weekly_revenue) / df_test$weekly_revenue)
#mean((exp(df_model7$pred) - df_model7$weekly_revenue) / df_model7$weekly_revenue)

```


log-log model where y = log_revenue, x1 = log_amazon stock price. x2 = log_price change.
```{r}
df_model7 <- subset(df, select = -c(week_id, store_id, pct_change_price, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, amzn_price))
# df_model7 <- transform(df_model8,inter=log_pct_change*max(Cultural,Sporting,National,Religious))
df_model7 <- df_model7[train_ind,]
df_test <- df_model7[-train_ind,]
model7 <- lm(log_weekly_revenue~.-weekly_revenue, data = df_model7)
summary(model7)
```

```{r}
df_test$pred <- predict(model7, newdata = df_test, type = 'response')
# mean((exp(df_test$pred)-exp(df_test$log_weekly_revenue))/exp(df_test$log_weekly_revenue))
mean((exp(df_test$pred) - df_test$weekly_revenue) / df_test$weekly_revenue)
```


Among model 5 to model 8, model 5 (log(y)~x1+x2)  and model 7 (log(y)~log(x1)+x2) provides the smallest relative error 1.29% and the highest Adj. R2 0.8374, 0.8375