Clear environment
```{r}
rm(list=ls())
gc(reset=TRUE)
```


Read in data and view first 6 rows
```{r}
data <- read.csv('../../Data/task_4_2.csv')
head(data)
dim(data)
```

Create interaction terms for all models
```{r}
data <- data %>%
  mutate(interaction_1 = pct_change_price*amzn_price) %>%
  mutate(interaction_2 = log_pct_change*log_amzn_price) %>%
  mutate(interaction_3 = pct_change_price*log_amzn_price) %>%
  mutate(interaction_4 = log_pct_change*amzn_price)
```



Train/test split, set seed to 273
```{r}
set.seed(8675309)
smpl.size <- floor(0.7 * nrow(data))
train_ind <- sample(nrow(data), size = smpl.size)
```

## Model 1
Train linear-linear model where y = revenue, x1 = amazon stock price (amzn_price), x2 = price change (pct_change_price)
```{r}
data_mod1 <- subset(data, select = -c(week_id, store_id, log_pct_change, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, log_amzn_price, log_weekly_revenue, interaction_2, interaction_3, interaction_4))
train_data_mod1 <- data_mod1[train_ind,]
val_data_mod1 <- data_mod1[-train_ind,]
mod1 <- lm(weekly_revenue~., data = train_data_mod1)
summary(mod1)
r2_1 <- summary(mod1)$adj.r.squared
```
Generate model plots - some issues in residuals vs fitted, Q-Q
```{r}
plot(mod1)
```


Calculate Cook's Distance for each observation to double check
```{r}
cooksD_mod1 <- cooks.distance(mod1)
```


Plot Cook's Distance to see observations that exceed threshold
```{r}
n <- nrow(data_mod1)
plot(cooksD_mod1, main = "Cooks Distance for Influential Obs")
which(cooksD_mod1 > 2)
```


Predict on validation data - mod1
```{r}
val_data_mod1$pred <- predict(mod1, newdata = val_data_mod1, type = 'response')

err1 <- mean((val_data_mod1$pred - val_data_mod1$weekly_revenue)/val_data_mod1$weekly_revenue)
err1
```


## Model 2
Train linear-log model where y = revenue, x1 = log amazon stock price (log_amzn_price), x2 = price change (log_pct_change)
```{r}
data_mod2 <- subset(data, select = -c(week_id, store_id, pct_change_price, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, amzn_price, log_weekly_revenue, interaction_1, interaction_3, interaction_4))
train_data_mod2 <- data_mod2[train_ind,]
val_data_mod2 <- data_mod2[-train_ind,]
mod2 <- lm(weekly_revenue~., data = train_data_mod2)
summary(mod2)
r2_2 <- summary(mod2)$adj.r.squared
```
Generate model plots - some issues in residuals vs fitted, Q-Q
```{r}
plot(mod2)
```


Calculate Cook's Distance for each observation to double check
```{r}
cooksD_mod2 <- cooks.distance(mod2)
```


Plot Cook's Distance to see observations that exceed threshold
```{r}
n <- nrow(data_mod2)
plot(cooksD_mod2, main = "Cooks Distance for Influential Obs")
which(cooksD_mod2 > 2)
```


Predict on validation data - mod2
```{r}
val_data_mod2$pred <- predict(mod2, newdata = val_data_mod2, type = 'response')

err2 <- mean((val_data_mod2$pred - val_data_mod2$weekly_revenue)/val_data_mod2$weekly_revenue)
err2
```


## Model 3
Train linear-log model where y = revenue, x1 = log amazon stock price (log_amzn_price), x2 = price change (pct_change_price)
```{r}
data_mod3 <- subset(data, select = -c(week_id, store_id, log_pct_change, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, amzn_price, log_weekly_revenue, interaction_1, interaction_2, interaction_4))
train_data_mod3 <- data_mod3[train_ind,]
val_data_mod3 <- data_mod3[-train_ind,]
mod3 <- lm(weekly_revenue~., data = train_data_mod3)
summary(mod3)
r2_3 <- summary(mod3)$adj.r.squared
```
Generate model plots - some issues in residuals vs fitted, Q-Q
```{r}
plot(mod3)
```


Calculate Cook's Distance for each observation to double check
```{r}
cooksD_mod3 <- cooks.distance(mod3)
```


Plot Cook's Distance to see observations that exceed threshold
```{r}
n <- nrow(data_mod3)
plot(cooksD_mod3, main = "Cooks Distance for Influential Obs")
which(cooksD_mod3 > 2)
```


Predict on validation data - mod3
```{r}
val_data_mod3$pred <- predict(mod3, newdata = val_data_mod3, type = 'response')

err3 <- mean((val_data_mod3$pred - val_data_mod3$weekly_revenue)/val_data_mod3$weekly_revenue)
err3
```


## Model 4
Train linear-log model where y = revenue, x1 = amazon stock price (amzn_price), x2 = log price change (log_pct_change)
```{r}
data_mod4 <- subset(data, select = -c(week_id, store_id, pct_change_price, store_id_WI_3, price_CA, price_WI, price_TX, gas_price, log_amzn_price, log_weekly_revenue, interaction_1, interaction_2, interaction_3))
train_data_mod4 <- data_mod4[train_ind,]
val_data_mod4 <- data_mod4[-train_ind,]
mod4 <- lm(weekly_revenue~., data = train_data_mod4)
summary(mod4)
r2_4 <- summary(mod4)$adj.r.squared
```
Generate model plots - some issues in residuals vs fitted, Q-Q
```{r}
plot(mod4)
```


Calculate Cook's Distance for each observation to double check
```{r}
cooksD_mod4 <- cooks.distance(mod4)
```


Plot Cook's Distance to see observations that exceed threshold
```{r}
n <- nrow(data_mod4)
plot(cooksD_mod4, main = "Cooks Distance for Influential Obs")
which(cooksD_mod4 > 2)
```


Predict on validation data - mod4
```{r}
val_data_mod4$pred <- predict(mod4, newdata = val_data_mod4, type = 'response')

err4 <- mean((val_data_mod4$pred - val_data_mod4$weekly_revenue)/val_data_mod4$weekly_revenue)
err4
```


## Summary
Output model validation metrics as summary
```{r}
df_summary <- data.frame("Model" = c("1","2","3","4"),
                         "ADJ_Rs" = c(r2_1,r2_2,r2_3,r2_4),
                         "Relative Error" = c(err1,err2,err3,err4))
df_summary
```
