
This is to create log_Y and log_X variables, please copy to the top of your part 2 modeling coding
```{r}
rm(list=ls())
gc(reset=TRUE)

if (!require(dplyr)) install.packages("dplyr")
library(dplyr)

walmart.sale <- read.csv("../../Data//task_4.csv")
```

```{r}
price <- read.csv('../../Data/sell_prices.csv')
head(price)
dim(price)
```

```{r}
on_shelf <- price %>% 
  mutate(on_shelf = ifelse(sell_price, 1, 0)) %>% 
  group_by(wm_yr_wk, store_id) %>% 
  summarise(item_on = sum(on_shelf))

head(on_shelf)
```


```{r}
walmart.sale <- transform(walmart.sale,log_amzn_price=log(amzn_price),log_weekly_revenue=log(weekly_revenue),log_gas_price = log(gas_price))

walmart.sale <- merge(walmart.sale, on_shelf, by = c('wm_yr_wk', 'store_id'))

walmart.sale.1 <- walmart.sale %>% 
                  filter(week_id %in% c(1:274))
walmart.sale.2 <- walmart.sale %>% 
                  filter(week_id %in% c(275:278))

write.csv(walmart.sale.1,"../../Data/task_4_2.csv", row.names = FALSE)
write.csv(walmart.sale.2,"../../Data/task_5.csv", row.names = FALSE)


```

read the dataframe
```{r}
if (!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)


head(walmart.sale)

```

scatter plot: Amazon stock price VS Walmart weekly revenue
```{r}
ggplot(walmart.sale, aes(x=amzn_price, y=weekly_revenue, color=store_id)) + geom_point() +
  labs(title="Amazon stock price VS Walmart weekly revenue", x="Amazon stock price", y="Walmart weekly revenue")+
  scale_colour_hue(l=50) + # Use a slightly darker palette than normal
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines
```

scatter plot: local gas price VS weekly revenue
```{r}
ggplot(walmart.sale, aes(x=gas_price, y=weekly_revenue,color=store_id)) + geom_point() +
  labs(title="Local Gas price VS Walmart weekly revenue", x="Local Gas Price", y="Walmart Weekly Revenue")+
  scale_colour_hue(l=30) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines
```

scatter plot: mean item price change VS weekly revenue
```{r}
ggplot(walmart.sale, aes(x=pct_change_price, y=weekly_revenue)) + geom_point() +
  labs(title="Mean Store Item Price Change VS Walmart Weekly Revenue", x="Mean Store Item Price Change", y="Walmart Weekly Revenue")+
  scale_colour_hue(l=30) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines

```

scatter plot: mean log item price change VS weekly revenue
```{r}
ggplot(walmart.sale, aes(x=log_pct_change, y=weekly_revenue)) + geom_point() +
  labs(title="Mean Log Store Item Price Change VS Walmart Weekly Revenue", x="Mean Log Store Item Price Change", y="Walmart Weekly Revenue")+
  scale_colour_hue(l=30) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines

```
```{r}
ggplot(walmart.sale, aes(x=week_id, y=weekly_revenue,color=store_id)) + geom_point() +
  labs(title="Walmart Weekly Revenue 2011-2016", x="Week 1 - Week 278", y="Walmart Weekly Revenue")+
  scale_colour_hue(l=30) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines
```

```{r}
ggplot(walmart.sale, aes(x=item_on, y=weekly_revenue,color=store_id)) + geom_point() +
  labs(title="Item On VS Walmart Weekly Revenue 2011-2016", x="Distinct Number of Items for Sale", y="Walmart Weekly Revenue")+
  scale_colour_hue(l=30) + 
  geom_smooth(method=lm,   # Add linear regression lines
              se=FALSE,    # Don't add shaded confidence region
              fullrange=TRUE) # Extend regression lines
```

Initial model and plotting
```{r}
rm(list=ls())
gc(reset=TRUE)
library(dplyr)

walmart.sale.total <- read.csv("../../Data/task_4_2.csv")

set.seed(6203)
samples <- sample(nrow(walmart.sale.total),size = floor(0.7 * nrow(walmart.sale.total)),replace=FALSE)
length(samples)
walmart.sale <- walmart.sale.total[samples,]
walmart.test <- walmart.sale.total[-samples,]

model.1 <- lm(weekly_revenue ~  store_id_CA_1+store_id_CA_2+store_id_CA_3+store_id_CA_4+store_id_TX_1+store_id_TX_2+store_id_TX_3+store_id_WI_1+store_id_WI_2+Cultural+Sporting+National+Religious+log_pct_change+amzn_price+item_on,data=walmart.sale)
plot(model.1)
summary(model.1)

walmart.test <- walmart.test %>% 
                  mutate(weekly_revenue_pred.1=predict(model.1,newdata=.,type="response"))  
      
model.1.val <- mean((walmart.test$weekly_revenue_pred.1-walmart.test$weekly_revenue)/walmart.test$weekly_revenue)



model.1.val


```

Cook distance >1 which get 


str(walmart.sale.2)



```{r}
cook_distance <-cooks.distance(model.1)

which(cook_distance >1)


```
calculate correlation:
youtube link: https://www.youtube.com/watch?v=8xpYrPqTBxs
```{r}

library(car)

cor_walmart <- cor(walmart.sale[,c(9:10,24,25,28)])
View(cor_walmart)

write.csv(cor_walmart,"../../Data/CorrelationTable.csv")
```


calculate PCA
youtube link: https://www.youtube.com/watch?v=xKl4LJAXnEA

```{r}
pca <- prcomp(t(walmart.sale[,c(9,24,25,28)]),scale=TRUE)
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100,1)
table <- data.frame(pca=pca$x,pca_per=pca.var.per)
barplot(pca.var.per,main="Screen Plot",xlab="Principle Component",ylab="Percent Variation")
View(table)
summary(pca)
```

```{r}
head(walmart.sale)
```


```{r}
pca2 <- prcomp(walmart.sale[,c(1, 3:7,9:28)],scale=TRUE)
summary(pca2)
plot(pca2, type='l')
```

```{r}
pca.var <- pca2$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100,1)
barplot(pca.var.per,main="Screen Plot",xlab="Principle Component",ylab="Percent Variation")
```

```{r}
df_pca <- as.data.frame(cbind(pca2$x[,1:14], walmart.sale[,8]))
head(df_pca)
```

```{r}
model_pca <- lm(V15~., data=df_pca)
summary(model_pca)
```

```{r}
beta <- model_pca$coefficients
alpha <- pca2$rotation[,1:14] %*% beta[2:15]
alpha0 <- alpha/sapply(walmart.sale[,c(1, 3:7,9:28)], sd)
beta0 <- beta[1] - sum(alpha*sapply(walmart.sale[,c(1, 3:7,9:28)], mean)/sapply(walmart.sale[,c(1, 3:7,9:28)],sd))
```

```{r}
alpha0
beta0
pred <- as.matrix(walmart.sale[,c(1, 3:7,9:28)]) %*% alpha0 + beta0
length(pred)
```

```{r}
SSre <- sum((pred - walmart.sale$weekly_revenue)^2)
SSto <- sum((walmart.sale$weekly_revenue-mean(walmart.sale$weekly_revenue))^2)
R2 <- 1 - SSre/SSto
R2
```

